### 2019-11-17 thesis/txt/0-introduction.tex
new data set name, change chapter 3 name, incorporate rest of annibales feedback

The goal of this thesis is to investigate different chunk retrieval techniques (CR techniques) for build logs and describe under which circumstances each techniques is recommended over another.
We aim to define a model to characterize different CR techniques, as well as the information retrievable from CI build logs.
For \textbf{RQ1}, we analyze which criteria influence the suitability of a CR technique for CI build logs.
We implement and evaluate three chunk retrieval techniques:
\begin{itemize}
  \item program synthesis by example using the Microsoft PROSE library (referred to as PBE),
  \item a common text similarity approach (referred to as CTS) and
  \item keyword search (referred to as KWS)
\end{itemize}
\textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited to retrieve information from continuous integration build logs.
\textbf{RQ2} is refined into sub-questions along with the criteria resulting from \textbf{RQ1} and compares their instantiations for the three techniques:
how many examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the configuring examples can be (\textbf{RQ2.2}) and the accuracy of the retrieved output (\textbf{RQ2.3}).
% \begin{simplebox}{Research Questions}
% \begin{itemize}
%   \item[\textbf{RQ1:}] Which criteria influence the suitability of a chunk retrieval technique for CI build logs?
%   \item[\textbf{RQ2:}] Under which conditions are PBE, CTS, and KWS suited to retrieve information from CI build logs?
%   \item[\textbf{RQ2.1:}] How many examples do PBE, CTS, and KWS need to perform best?
%   \item[\textbf{RQ2.2:}] How structurally similar do the examples for PBE, CTS and KWS need to be for the techniques to be applicable?
%   \item[\textbf{RQ2.3:}] How accurate are the retrievals of PBE, CTS, and KWS?
% \end{itemize}
% \end{simplebox}
To evaluate PBE, CTS and KWS we create a dataset, namely the \emph{Failing Build Logs Data Set}, which encompasses about 800 log files from 80 repositories.
Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural position within the log.

Our study of the three techniques on \emph{Failing Build Logs Data Set} shows that
\begin{itemize}
  \item PBE yields very accurate results when configured with 1 to 3 examples from a single structural category.
  \item CTS shows the best average precision, though the quality of the retrieval is hard to determine from a given result.
  A small increase in the number of examples used in the configuration has no visible influence and fewer structural categories improve the retrieval accuracy.
  \item KWS has the highest recall of all techniques combined with much lower recall.
  It is the only technique where retrieval quality does not decrease with an increasing number of structural categories in the configuring examples.
\end{itemize}
We recommend PBE for use cases where the desired information is always represented in the same structurally predictable way and high confidence in the exactness of the chunk retrieval is required.
CTS is well suited when the representation of the desired information varies slightly and the output of the chunk retrieval is further processed by a human.
In cases where the representation fo the desired information is unpredictable or varies greatly, KWS is the best technique to choose.
However, the low precision requires a human to interpret the output of the chunk retrieval.

@@

This thesis first presents an overview of related research, spanning from CI, build log analysis and augmentation, and common system log processing over information retrieval techniques to program synthesis by examples.
Next, chapter~\ref{sec:techniques} characterizes chunk retrieval techniques and retrievable information from CI build logs.
It also introduces the three investigated techniques: PBE, CTS and KWS\@.
Chapter~\ref{sec:data-set} describes the creation of the \emph{Failing Build Logs Data Set} collected from failed Travis CI build logs, including the labeling and the validation process.
Following, Chapter~\ref{sec:implementation} outlines our implementation of the three chosen chunk retrieval techniques and the usage of our unified chunk retrieval tool.
This tool is also used for the evaluation study of our models described in Chapter~\ref{sec:study}.
Chapter~\ref{sec:discussion} discusses the implications of the study results and recommendations on when PBE, CTS and KWS are most suitable.
Lastly, we conclude and give an overview of further research opportunities in Chapter~\ref{sec:conclusion}.
\end{document}

>>>>

The goal of this thesis is to investigate different chunk retrieval techniques (CR techniques) for build logs and describe under which circumstances each techniques is recommended over another.
We aim to define a model to characterize different CR techniques, as well as the information retrievable from CI build logs.
For \textbf{RQ1}, we analyze which criteria influence the suitability of a CR technique for CI build logs.
We implement and evaluate three chunk retrieval techniques:
\begin{itemize}
  \item program synthesis by example using the Microsoft PROSE library (referred to as PBE),
  \item a common text similarity approach (referred to as CTS) and
  \item keyword search (referred to as KWS)
\end{itemize}
\textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited to retrieve information from continuous integration build logs.
\textbf{RQ2} is refined into sub-questions along with the criteria resulting from \textbf{RQ1} and compares their instantiations for the three techniques:
how many examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the examples can be (\textbf{RQ2.2}) and the accuracy of the retrieved output (\textbf{RQ2.3}).
% \begin{simplebox}{Research Questions}
% \begin{itemize}
%   \item[\textbf{RQ1:}] Which criteria influence the suitability of a chunk retrieval technique for CI build logs?
%   \item[\textbf{RQ2:}] Under which conditions are PBE, CTS, and KWS suited to retrieve information from CI build logs?
%   \item[\textbf{RQ2.1:}] How many examples do PBE, CTS, and KWS need to perform best?
%   \item[\textbf{RQ2.2:}] How structurally similar do the examples for PBE, CTS and KWS need to be for the techniques to be applicable?
%   \item[\textbf{RQ2.3:}] How accurate are the retrievals of PBE, CTS, and KWS?
% \end{itemize}
% \end{simplebox}
To evaluate PBE, CTS and KWS we create a data set, namely \emph{LogChunks}, which encompasses about 800 log files from 80 repositories.
Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural position within the log.

Our study of the three techniques on \emph{LogChunks} shows that
\begin{itemize}
  \item PBE yields very accurate results when configured with 1 to 3 examples from a single structural category.
  \item CTS shows the best average precision, though the quality of the retrieval is hard to determine from a given result.
  A small increase in the number of examples used in the configuration has no visible influence and fewer structural categories improve the retrieval accuracy.
  \item KWS has the highest recall of all techniques combined with much lower recall.
  It is the only technique where retrieval quality does not decrease with an increasing number of structural categories in the configuring examples.
\end{itemize}
We recommend PBE for use cases where the desired information is always represented in the same structurally predictable way and high confidence in the exactness of the chunk retrieval is required.
CTS is well suited when the representation of the desired information varies slightly and the output of the chunk retrieval is further processed by a human.
In cases where the textual representation of the desired information in the log is unpredictable or varies greatly, KWS is the best technique to choose.
However, the low precision requires a human to interpret the output of the chunk retrieval.

@@

This thesis first presents an overview of related research, spanning from CI, build log analysis and augmentation to system log processing.
Chapter~\ref{sec:rw} presents existing work on information extraction and retrieval techniques and program synthesis from examples.
Next, Chapter~\ref{sec:techniques} characterizes chunk retrieval techniques and retrievable information from CI build logs.
It also introduces the three investigated techniques: PBE, CTS and KWS\@.
Chapter~\ref{sec:data-set} describes the creation of the \emph{LogChunks} data set collected from failed Travis CI build logs, including the labeling and the validation process.
Following, Chapter~\ref{sec:implementation} outlines our implementation of the three chosen chunk retrieval techniques and the usage of our unified chunk retrieval tool.
This tool is also used for the evaluation study of our models described in Chapter~\ref{sec:study}.
Chapter~\ref{sec:discussion} discusses the implications of the study results and recommendations on when PBE, CTS and KWS are most suitable.
Lastly, we conclude and give an overview of further research opportunities in Chapter~\ref{sec:conclusion}.
\end{document}

### 2019-11-17 thesis/txt/1-related-work.tex
new data set name, change chapter 3 name, incorporate rest of annibales feedback

\chapter{Background}
\plan{all of RW: 4 - 5 pages left to do + some research!}
\plan{write, 1/3 page, blocked by: other sections}
\label{sec:rw}
This section presents various research works adjacent or foundational to our work.
Starting with studies about Continuous Integration used in software projects, we move on to past works about build log analysis and their augmentation.
We differentiate our work from the more common system log analysis and show how we classify build logs as semi-structured data.
We cover different information retrieval and extraction techniques \todo{half sentence missing: specify which techniques? 'used in software reasearch' 'used to assist software engineers'}.
Lastly this section mentions different Programming by Example resources surrounding Microsoft's work on the PROSE library.
\todo{do we also mention more things?}
% moritz: nice formulation :)

@@

The structure of build logs
\begin{itemize}
  \item \textbf{is implicit}.
  We might not have access to explicit structuring elements or an explicit structure description.
  Computation is required to infer the present structure.
  \item \textbf{is irregular}.
  Changes in the build process or execution environment might change the structure of a build log.
  We observed this in the logs we collected for the \emph{Failing Build Log Data Set}, where for the same repository and build configuration some logs had double new line characters without any noticeable explanation.
  You can see an example of this in Figure~\ref{fig:log-4} and Figure~\ref{fig:log-5}.
  \item \textbf{is partial}. Some parts are highly structured by e.g.\ structure indicating special characters and others are unstructured, e.g.\ natural language text in error messages.
  \item can be described with an \textbf{analytical data guide} rather than a beforehand defined schema.
  There is no fixed specification on how build tools structure their output.
  We afterwards extract structuring patterns in the produced output.
  \item \textbf{has a rapidly evolving schema}.
  Modifications in the build configuration might change the tools involved in the build and therefore the composition of the build log.
  Previous work indicates that some projects change their CI configuration often~\cite{hilton2016usage} and software tools adopt their log messages over time~\cite{yuan2012characterizing}.
\end{itemize}

>>>>

\chapter{Background}
\plan{whole RW currently highly work in progress, text not yet coherent!}
\plan{all of RW: 4 - 5 pages left to do + some research!}
\plan{write, 1/3 page, blocked by: other sections}
\label{sec:rw}
This section presents various research works adjacent or foundational to our work.
Starting with studies about Continuous Integration used in software projects, we move on to past works about build log analysis and their augmentation.
We differentiate our work from the more common system log analysis and show how we classify build logs as semi-structured data.
We cover different information retrieval and extraction techniques \todo{half sentence missing: specify which techniques? 'used in software reasearch' 'used to assist software engineers'}.
Lastly this section mentions different Programming by Example resources surrounding Microsoft's work on the PROSE library.
\todo{do we also mention more things?}
% moritz: nice formulation :)

@@

The structure of build logs
\begin{itemize}
  \item \textbf{is implicit}.
  We might not have access to explicit structuring elements or an explicit structure description.
  Computation is required to infer the present structure.
  \item \textbf{is irregular}.
  Changes in the build process or execution environment might change the structure of a build log.
  We observed this in the logs we collected for the \emph{LogChunks} data set, where for the same repository and build configuration some logs had double new line characters without any noticeable explanation.
  You can see an example of this in Figure~\ref{fig:log-4} and Figure~\ref{fig:log-5}.
  \item \textbf{is partial}. Some parts are highly structured by e.g.\ structure indicating special characters and others are unstructured, e.g.\ natural language text in error messages.
  \item can be described with an \textbf{analytical data guide} rather than a beforehand defined schema.
  There is no fixed specification on how build tools structure their output.
  We afterwards extract structuring patterns in the produced output.
  \item \textbf{has a rapidly evolving schema}.
  Modifications in the build configuration might change the tools involved in the build and therefore the composition of the build log.
  Previous work indicates that some projects change their CI configuration often~\cite{hilton2016usage} and software tools adopt their log messages over time~\cite{yuan2012characterizing}.
\end{itemize}

### 2019-11-17 thesis/txt/2-models.tex
new data set name, change chapter 3 name, incorporate rest of annibales feedback

\chapter{Chunk Retrieval Techniques for Build Logs}
\label{sec:techniques}
This chapter presents how a build log is created by a continuous integration (CI) build.
It explains our notion of retrievable information contained in build logs.
We introduce our notion of chunk retrieval techniques to retrieve information from build logs and present the three chunk retrieval techniques we investigate for this thesis:
Program synthesis by example (PBE), common text similarity (CTS) and keyword search (KWS).

@@

During our initial exploration and log data collection for the \emph{Failing Build Log Data Set}, we collected a broad set of build logs from 29 languages and 87 repositories from Travis CI~\cite{travisci2019webpage}.
We inspected them to get an impression about the information one would want to retrieve from a build log.
In the following, we describe the possibly interesting information types to be retrieved from Travis CI build logs.
All BLIs containing ``Travis'' in their name are specific to Travis CI build logs, the others can also apply to build logs from another CI environment.
Figure~\ref{fig:build-log-information} shows an overview of these BLIs.

@@

\subsection{Keyword Search (KWS)}
\label{sec:expl-skws}
When developers are looking for a specific piece of information within a great amount of unstructured information, they search for related keywords as a first ad-hoc approach.
This was one of the most common approaches we took when searching for the build failure reason within a log when creating our \emph{Failing Build Logs Data Set}.
As this is a technique readily available in many tools developers use to view build logs, we want to study when such a keyword search is recommendable for retrieving information chunks from CI build logs.
In the following we will explain how we use simple keyword search to retrieve information from CI build logs (KWS), the concrete implementation is described in~\ref{sec:impl-skws}.
%Figure~\ref{fig:keyword-search-explanation} shows the instantiation of the BLIRT model for SKWS.

>>>>

\chapter{Introduction to Chunk Retrieval Techniques}
\label{sec:techniques}
This chapter presents how a build log is created by a continuous integration (CI) build.
It explains our notion of retrievable information contained in build logs.
We introduce our notion of chunk retrieval techniques to retrieve information from build logs and present the three chunk retrieval techniques we investigate for this thesis:
Program synthesis by example (PBE), common text similarity (CTS) and keyword search (KWS).

@@

During our initial exploration and log data collection for the \emph{LogChunks} data set, we collected a broad set of build logs from 29 languages and 87 repositories from Travis CI~\cite{travisci2019webpage}.
We inspected them to get an impression about the information one would want to retrieve from a build log.
In the following, we describe the possibly interesting information types to be retrieved from Travis CI build logs.
All BLIs containing ``Travis'' in their name are specific to Travis CI build logs, the others can also apply to build logs from another CI environment.
Figure~\ref{fig:build-log-information} shows an overview of these BLIs.

@@

\subsection{Keyword Search (KWS)}
\label{sec:expl-skws}
When developers are looking for a specific piece of information within a great amount of unstructured information, they search for related keywords as a first ad-hoc approach.
This was one of the most common approaches we took when searching for the build failure reason within a log when creating our \emph{LogChunks} data set.
As this is a technique readily available in many tools developers use to view build logs, we want to study when such a keyword search is recommendable for retrieving information chunks from CI build logs.
In the following we will explain how we use simple keyword search to retrieve information from CI build logs (KWS), the concrete implementation is described in~\ref{sec:impl-skws}.
%Figure~\ref{fig:keyword-search-explanation} shows the instantiation of the BLIRT model for SKWS.

### 2019-11-17 thesis/txt/3-data-set.tex
new data set name, change chapter 3 name, incorporate rest of annibales feedback

\chapter{BUILDS - BUIld Log Data Set}
\includegraphics[page=5, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}

@@

% \section{Collection Process}
% For our initial data collection to get an impression of build logs from various projects and languages we used the \texttt{LogCollector} to gather from the 30 most popular languages, up to 3 repositories using Travis CI each and 3 logs per state for each of those repositories.
% For the \emph{Failing Build Log Data Set} we again collected from the same selection of repositories though saved only 10 logs of the state \emph{failed} for each repository.
% our impression?
% \todo{image!}

@@

\subsection{Inter-Rater Reliability}
re-labeling of parts of the labels - cohen's kappa
\subsubsection{Introduction}
\subsubsection{Method}
\subsubsection{Results}
\subsubsection{Discussion}
\subsubsection{Threats to Validity}

\subsection{Developer Survey}
\subsubsection{Introduction}
For the \emph{Failing Build Log Data Set} we analyzed around 800 build logs from different repositories and tried to extract the part of the log which describes why the respective build failed.
As we are not involved in the development of any of the open source projects within our data set we could only rely on our previous experience with different build logs and systems.
We only looked into the logs and did not check the related configurations, so it is well possible that we extracted parts that do describe errors but the respective step failing is ignored by the configuration and the build failed for another reason.

The person who probably knows best why a build failed is the one committing the changes which triggered the build.
If the build was e.g.\ part of a pull request then developer likely looked at it and tried to fix it so the pull request could be accepted.
In this section we describe how we validate the extractions of the build failure reason the \emph{Failing Build Log Data Set} describes.
\subsubsection{Method}
Using the Travis API, for every build log in the data set we looked up the corresponding build and the committer information.
We grouped all commits triggered by one developer and sent out an email to each of them, asking whether the log part selected during our labeling was indeed describing the reason the build failed.Figure~\ref{fig:dev-mail} shows one of the mails sent out.
The email included links to the corresponding commits, build overview and log file.
We asked the receivers to fill out a short survey in case our extraction was not correct.
Look at Figure~\ref{fig:dev-survey} to get an impression of the survey.
In the survey we presented the selected log part and asked the developer to paste in the log part actually describing the failure reason or describe why we were wrong in their own words.
As some of the extractions we labeled are many lines long, we trimmed all down to 10 lines in order to keep the mail readable.

@@

\subsubsection{Discussion}
This study highly strengthens the trust in the validity of the extracted build failure reasons in the \emph{Failing Build Log Data Set}.
The study received answers about 18\% of the logs labelled in our build log, of which, after manual correction, 91\% said our labelled extractions were accurate.

>>>>

\chapter{LogChunks Data Set}
\includegraphics[page=5, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}

@@

% \section{Collection Process}
% For our initial data collection to get an impression of build logs from various projects and languages we used the \texttt{LogCollector} to gather from the 30 most popular languages, up to 3 repositories using Travis CI each and 3 logs per state for each of those repositories.
% For \emph{LogChunks} we again collected from the same selection of repositories though saved only 10 logs of the state \emph{failed} for each repository.
% our impression?
% \todo{image!}

@@

\subsection{Inter-Rater Reliability}
re-labeling of parts of the labels - cohen's kappa
\subsubsection{Introduction}
After the manual labeling of the data set we performed a second labeling of a sample of the build logs to validate the labels.
\subsubsection{Method}
For each label category: Build Failure Reason, keywords and category, we relabeled 30 randomly sampled logs.
compared the labeles, \todo{discussed about it}.
\subsubsection{Results}

\subsubsection{Discussion}
main takeaway: overlap yes, but high variation

build failure reason: should we extract the information \emph{that} the build failed as well?
our data set extracts the parts describing \emph{why}, but leaves out the lines stating that the build failed (e.g. step xy exited with 1).

keywords: first labeler allowed also longer strings with spaces and adhered to capitalization.
second one ignored captialization and focussed on the keyword.
so only one word was allowed.
also the first one labeled always a full repository at a time.
so could take into consideration patterns and see what keywords are exception specific and would only retrieve the failure reason if this specific exception occured.
second labeler only one build log excerpt (+ context) per repository.
also: influene of ansi color codes ``merror'' vs. ``error'' first labeler known as ansi color codes, second one counted it into the word (whole word always)
first was also more inclined to search for a subpart of a word to make it more generalizeable (``failure`` instead of ``failures'')

categories: description for the second labeling stated: sort into categories on why build failed.
was exectued with sorting into test/linter/compilation.
in the case of the selected repositories everything was labeled as test. mostly correct (one linter), but more importantly no difference was made in which test step failed / how the failed tests were represented.
the categories are thought as structural categories.
so the surrounding sturcture and the way a test failure is communicated is important. e.g. if several tests are run then it is important which ones failed

main influence / implication: the labels we select are not black/white. accurate description of what we do is very very important. mainly influenced how we described our data points in the earlier sections.
\subsubsection{Threats to Validity}

\subsection{Developer Survey}
\subsubsection{Introduction}
For \emph{LogChunks} we analyzed around 800 build logs from different repositories and tried to extract the part of the log which describes why the respective build failed.
As we are not involved in the development of any of the open source projects within our data set we could only rely on our previous experience with different build logs and systems.
We only looked into the logs and did not check the related configurations, so it is well possible that we extracted parts that do describe errors but the respective step failing is ignored by the configuration and the build failed for another reason.

The person who probably knows best why a build failed is the one committing the changes which triggered the build.
If the build was e.g.\ part of a pull request then developer likely looked at it and tried to fix it so the pull request could be accepted.
In this section we describe how we validate the extractions of the build failure reason \emph{LogChunks} describes.
\subsubsection{Method}
Using the Travis API, for every build log in the data set we looked up the corresponding build and the committer information.
We grouped all commits triggered by one developer and sent out an email to each of them, asking whether the log part selected during our labeling was indeed describing the reason the build failed.Figure~\ref{fig:dev-mail} shows one of the mails sent out.
The email included links to the corresponding commits, build overview and log file.
We asked the receivers to fill out a short survey in case our extraction was not correct.
Look at Figure~\ref{fig:dev-survey} to get an impression of the survey.
In the survey we presented the selected log part and asked the developer to paste in the log part actually describing the failure reason or describe why we were wrong in their own words.
As some of the extractions we labeled are many lines long, we trimmed all down to 10 lines in order to keep the mail readable.

@@

\subsubsection{Discussion}
This study highly strengthens the trust in the validity of the extracted build failure reasons in \emph{LogChunks}.
The study received answers about 18\% of the logs labelled in our build log, of which, after manual correction, 91\% said our labelled extractions were accurate.

### 2019-11-17 thesis/txt/4-tool.tex
first half of prose rw section
write about last ci papers, fix references
new data set name, change chapter 3 name, incorporate rest of annibales feedback

\chapter{Tool Implementation}
\label{sec:implementation}
To evaluate PBE, CTS and KWS on the \emph{Failing Build Log Data Set} we implemented them and a unifying interface to retrieve chunks from build logs.

@@

To retrieve chunks from a build log use the option \texttt{-a analyze} with these options:
\begin{itemize}
    \item \texttt{-t} \textbf{Technique} \texttt{pbe, ir, keyword or random}. Specify which technique to use for extraction.
    \item \texttt{-e} \textbf{Examples Set} The example set used to configure the technique. For pbe, ir and random analysis only. See Section \ref{sec:todo} for the definition of an example set.
    \item \texttt{-p} \textbf{Build Log Path} The path to the file to be analyzed.
    \item \texttt{-k} \textbf{Keywords} The keywords to search for, only for keyword analysis.
\end{itemize}

To evaluate a CTR use the option \textttt{-a evaluate} with these options:
\begin{itemize}
    \item \texttt{-t} \textbf{Technique} \texttt{pbe, ir, keyword or random}. Specify which technique to use for extraction.
    \item \texttt{-e} \textbf{Examples Set} The example set used to configure the technique. See Section \ref{sec:todo} for the definition of an example set.
    \item \texttt{-s} \textbf{Selection Technique} \texttt{chronological, random or manual} How the order of the examples should be selected during learning.
    Manual selects the examples according to the sequence defined in the example set file.
    \item \texttt{-l} \textbf{Learning Step Count} How many learning steps should be evaluated, the maximum number of examples to learn with.
    The referenced example set must define at least \emph{Learning Step Count + Test Count} examples.
    \item \texttt{-t} \textbf{Test Count} On how many following examples the learned technique should be tested.
    Currently only \texttt{1} is supported.
\end{itemize}

>>>>

\chapter{Tool Implementation}
\label{sec:implementation}
To evaluate PBE, CTS and KWS on \emph{LogChunks} we implemented them and a unifying interface to retrieve chunks from build logs.

@@

To retrieve chunks from a build log use the option \texttt{-a analyze} with these options:
\begin{itemize}
    \item \texttt{-t} \textbf{Technique} \texttt{pbe, ir, keyword or random}. Specify which technique to use for extraction.
    \item \texttt{-e} \textbf{Examples Set} The example set used to configure the technique. For pbe, ir and random analysis only. See Section \ref{sec:example-set} for the definition of an example set.
    \item \texttt{-p} \textbf{Build Log Path} The path to the file to be analyzed.
    \item \texttt{-k} \textbf{Keywords} The keywords to search for, only for keyword analysis.
\end{itemize}

To evaluate a CTR use the option \texttt{-a evaluate} with these options:
\begin{itemize}
    \item \texttt{-t} \textbf{Technique} \texttt{pbe, ir, keyword or random}. Specify which technique to use for extraction.
    \item \texttt{-e} \textbf{Examples Set} The example set used to configure the technique. See Section \ref{sec:example-set} for the definition of an example set.
    \item \texttt{-s} \textbf{Selection Technique} \texttt{chronological, random or manual} How the order of the examples should be selected during learning.
    Manual selects the examples according to the sequence defined in the example set file.
    \item \texttt{-l} \textbf{Learning Step Count} How many learning steps should be evaluated, the maximum number of examples to learn with.
    The referenced example set must define at least \emph{Learning Step Count + Test Count} examples.
    \item \texttt{-t} \textbf{Test Count} On how many following examples the learned technique should be tested.
    Currently only \texttt{1} is supported.
\end{itemize}

### 2019-11-17 thesis/txt/5-study.tex
change easy feedback from moritz paper review
new data set name, change chapter 3 name, incorporate rest of annibales feedback

\chapter{Empirical Comparison Study}
\label{sec:study}
To investigate when PBE, CTS and KWS are suited to retrieve chunks from CI build logs we evaluated our implementation of those techniques on the \emph{Failing Build Log Data Set}.
This chapter describes our study design and presents the results of the study.
The analysis of the study results first focusses on each of the three techniques and later we compare them against each other.

@@

\section{Study Design}
For the comparison study we evaluate the three chunk retrieval techniques PBE, CTS and KWS, described in Sections~\ref{sec:expl-pbe},\ref{sec:expl-ts} and~\ref{sec:expl-skws}.
RLR, explained in Section~\ref{sec:expl-rlr}, acts as a baseline for the comparison.
We run four techniques on the example sets from the \emph{Failing Build Log Data Set}.

@@

%taking The Failing Build Log Data Set - run 3(4 with random) techniques with increasing example count - measuring xyz - justify choices like running chronologically / testing on 1 example / no k-fold validation - how are keywords for the search selected?

@@

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-PBE.pdf}
		\caption{Results of chunk retrieval with PBE}
		\label{fig:failure-reason-PBE}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
		\caption{Results of chunk retrieval with PBE for numbers of categories present in configuring I/O examples}
		\label{fig:failure-reason-categorycount-PBE}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-extraction-result-PBE.pdf}
		\caption{Precision of chunk retrieval with PBE for increasing count of configuring I/O examples}
		\label{fig:precision-extraction-result-PBE}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
		\caption{xxx}
		\label{fig:xxx}
	\end{minipage}
\end{figure}
\subsection{Regular Expression Program Synthesis by Example (PBE)}
Figure~\ref{fig:failure-reason-PBE} shows the results of the PBE runs in our evaluation.
Out of the 400 runs, 5 per each one of the 80 example sets, PBE extracted all the desired lines in 138 cases.
Figure~\ref{fig:failure-reason-PBE} shows that in 89 further cases a program was also successfully synthesized, though in 59 cases the synthesized program yielded no output at all.
In 30 cases the synthesized program did not extract all of the desired lines, though still had an average recall of 28\%.
In 173 cases the PROSE program synthesis could not synthesize a singular regular expression program that satisfies all of the configuring I/O examples.

>>>>

\chapter{Empirical Comparison Study}
\label{sec:study}
To investigate when PBE, CTS and KWS are suited to retrieve chunks from CI build logs we evaluated our implementation of those techniques on the \emph{LogChunks} data set.
This chapter describes our study design and presents the results of the study.
The analysis of the study results first focusses on each of the three techniques and later we compare them against each other.

@@

\section{Study Design}
For the comparison study we evaluate the three chunk retrieval techniques PBE, CTS and KWS, described in Sections~\ref{sec:expl-pbe},\ref{sec:expl-ts} and~\ref{sec:expl-skws}.
RLR, explained in Section~\ref{sec:expl-rlr}, acts as a baseline for the comparison.
We run four techniques on the example sets from \emph{LogChunks}.

@@

%taking The LogChunks data Set - run 3(4 with random) techniques with increasing example count - measuring xyz - justify choices like running chronologically / testing on 1 example / no k-fold validation - how are keywords for the search selected?

@@

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-PBE.pdf}
		\caption{Results of chunk retrieval with PBE}
		\label{fig:failure-reason-PBE}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
		\caption{Results of chunk retrieval with PBE for numbers of categories present in configuring I/O examples}
		\label{fig:failure-reason-categorycount-PBE}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-extraction-result-PBE.pdf}
		\caption{Precision of chunk retrieval with PBE for increasing count of configuring I/O examples}
		\label{fig:precision-extraction-result-PBE}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
		\caption{xxx}
		\label{fig:xxx}
	\end{minipage}
\end{figure}
\subsection{Program Synthesis by Example (PBE)}
Figure~\ref{fig:failure-reason-PBE} shows the results of the PBE runs in our evaluation.
Out of the 400 runs, 5 per each one of the 80 example sets, PBE extracted all the desired lines in 138 cases.
Figure~\ref{fig:failure-reason-PBE} shows that in 89 further cases a program was also successfully synthesized, though in 59 cases the synthesized program yielded no output at all.
In 30 cases the synthesized program did not extract all of the desired lines, though still had an average recall of 28\%.
In 173 cases the PROSE program synthesis could not synthesize a singular regular expression program that satisfies all of the configuring I/O examples.
